### 2015-05-13 stat302/hw4.tex
Finished problem 2, hw4

                \includegraphics[width=9cm]{hw4/pr1_vi_hist_a}
                \includegraphics[width=9cm]{hw4/pr1_vi_hist_b} \\
                \includegraphics[width=9cm]{hw4/pr1_vi_hist_c} \\

@@

                \includegraphics[width=9cm]{hw4/pr1_vii_hist_a}
                \includegraphics[width=9cm]{hw4/pr1_vii_hist_b} \\
                \includegraphics[width=9cm]{hw4/pr1_vii_hist_c} \\

@@

>>>>

                \includegraphics[width=9cm]{hw4/pr1_vi_a}
                \includegraphics[width=9cm]{hw4/pr1_vi_b} \\
                \includegraphics[width=9cm]{hw4/pr1_vi_c} \\

@@

                \includegraphics[width=9cm]{hw4/pr1_vii_a}
                \includegraphics[width=9cm]{hw4/pr1_vii_b} \\
                \includegraphics[width=9cm]{hw4/pr1_vii_c} \\

@@

        \end{itemize}
    \item[2.]
                Repeating the same procedure as above, except with reject decisions based on q values, I get these results: \\
                \includegraphics[width=9cm]{hw4/pr2_i_FDR_a}
                \includegraphics[width=9cm]{hw4/pr2_i_pFDR_a} \\
                In this first scenario, the FDR seems to be controlled at pretty much exactly the desired rate, while the pFDR is still necessarily 1.\\
                \includegraphics[width=9cm]{hw4/pr2_i_FDR_b}
                \includegraphics[width=9cm]{hw4/pr2_i_pFDR_b} \\
                In this second scenario, we have control of both FDR and pFDR at the desired rate.\\
                \includegraphics[width=9cm]{hw4/pr2_i_FDR_c}
                \includegraphics[width=9cm]{hw4/pr2_i_pFDR_c} \\
                With no false discoveries, FDR and pFDR are still 0.
            \item[2)]
                I have plotted the estimated $\pi_0$ vs actual $\pi_0$ over a range of values for $\sigma_b=.5,1,2,4$. Each estimate is the average over 100 simulations. \\
                \includegraphics[width=9cm]{hw4/pr2_ii_pt5}
                \includegraphics[width=9cm]{hw4/pr2_ii_1}\\
                As we can see above and below, the estimates get increasingly good as the variance goes up and the $\beta$ tend to fall farther from $0$. The predictions are uniformly higher than the actual $\pi_0$, except for values near 1, and the worst predictions are for low values of $\pi_0$. In general, this method seem to provide a pretty solid estimate. \\
                \includegraphics[width=9cm]{hw4/pr2_ii_2}
                \includegraphics[width=9cm]{hw4/pr2_ii_4}\\
